On Secure Delegation of SampBQP with a Classical Client

### 2020-03-29 hamiltonian.tex
Get ready for next round of feedbacks
Make V_Ham fidelity lemma work for mixed states

\begin{algorithm}
	\caption{Check for ground state $\cVGS$}
	\label{AlgGroundStateCheck}
		Let $H=\sum_{S\in\mathcal{G}_{XZ}} d_S S$.
		Let $\ket\phi$ be the potential ground state to check.
		\begin{itemize}
			\item Set $D = \sum_{S\in\mathcal{G}_{XZ}}|d_S|$
			\item Set $p_S = \frac{|d_S|}{D}$
			\item Sample $\widetilde{S}$ from $\mathcal{G}_{XZ}$, weighted by $p_S$.
			\item Measure $\ket\phi$ in the $\widetilde{S}$ basis, recording the result as $\lambda_{\widetilde{S}}$.
			\item If $\sgn(d_{\widetilde{S}})\lambda_{\widetilde{S}}=-1$, accept. Otherwise, reject.
		\end{itemize}
\end{algorithm}

@@

	\label{cor:HamCheck}
	There exists some $c\in\bbR$ s.t.
	let $H_{C(x)}$ be as above and
	$\varepsilon\in\bbR$, then
	if $\cVGS$ accepts $\rho$ with probability at least $\frac{1}{2}-\frac{c\varepsilon}{T^5}$
	then $F(\rho, \psi_{C(x)})\geq1-\varepsilon$
\end{cor}
\begin{prf}
	Define $c$ so that $\cVGS$ accepts $\ket{\phi}$ with probability $\frac{1}{2}-\frac{c}{T^5}\braket{\phi|H_{C(x)}|\phi}$.

	Break $\ket{\phi}$ above into what's in the kernel of $H$ and what isn't.
	$$\ket{\phi}=\braket{\psi_{C(x)}|\phi}\ket{\phi_K}+\sqrt{1-\abs{\braket{\psi_{C(x)}|\phi}}^2}\ket{\phi_{K^\bot}}$$
	We can then see $\braket{\phi|H|\phi}=1-\abs{\braket{\psi_{C(x)}|\phi}}^2=1-F(\psi_{C(x)}, \phi)$.

	Now we have
	$$p_{acc}=\frac{1}{2}-\frac{c}{T^5}(1-F(\psi_{C(x)}, \phi))\geq\frac{1}{2}-\frac{c\varepsilon}{T^5}$$
	which easily implies our claim for pure state inputs $\phi$.

	The argument generalizes easily to mixed state inputs $\rho$.
\end{prf}

>>>>

\begin{algorithm}
	\caption{Check for ground state $\cVGS$}
	\label{AlgGroundStateCheck}
		Let $H=\sum_{S\in\mathcal{G}_{XZ}} d_S S$.
		Let $\ket\phi$ be the potential ground state to check.
		\begin{itemize}
			\item Set $D = \sum_{S\in\mathcal{G}_{XZ}}|d_S|$
			\item Set $p_S = \frac{|d_S|}{D}$
			\item Sample $\widetilde{S}$ from $\mathcal{G}_{XZ}$, weighted by $p_S$.
			\item Measure $\ket\phi$ in the $\widetilde{S}$ basis, recording the result as $\lambda_{\widetilde{S}}$.
			\item If $\sgn(d_{\widetilde{S}})\lambda_{\widetilde{S}}=-1$, accept by outputting $1$. Otherwise, reject by outputting $0$.
		\end{itemize}
\end{algorithm}

@@

	\label{cor:HamCheck}
	There exists some $c\in\bbR$ s.t.
	let $H_{C(x)}$ be as above and
	$\varepsilon\in\bbR$, then
	if $\cVGS(\rho)$ accepts with probability at least $\frac{1}{2}-\frac{c\varepsilon}{T^5}$
	then $F(\rho, \ket{\psi_{C(x)}})\geq1-\varepsilon$
\end{cor}
\begin{prf}
	We first argue this with pure state input $\ket\phi$.

	Define $c$ so that $\cVGS$ accepts $\ket{\phi}$ with probability $\frac{1}{2}-\frac{c}{T^5}\braket{\phi|H_{C(x)}|\phi}$.
	Break $\ket{\phi}$ above into what's in the kernel of $H$ and what isn't:
	$$\ket{\phi}=\braket{\psi_{C(x)}|\phi}\ket{\phi_K}+\sqrt{1-\abs{\braket{\psi_{C(x)}|\phi}}^2}\ket{\phi_{K^\bot}}$$
	We can then see $\braket{\phi|H|\phi}=1-\abs{\braket{\psi_{C(x)}|\phi}}^2=1-F(\ket{\psi_{C(x)}}, \ket{\phi})$.
	This argument above can be generalized for mixed states since we have for all $\sigma$ that
	$$F(\sum_i p_i \ket{\phi_i}\bra{\phi_i}, \sigma)=\sum_i p_i F(\ket{\phi_i}, \sigma)$$
	Now we have
	$$p_{acc}=\frac{1}{2}-\frac{c}{T^5}(1-F(\ket{\psi_{C(x)}}, \rho))\geq\frac{1}{2}-\frac{c\varepsilon}{T^5}$$
	which implies our claim.
\end{prf}
